```{r}
library(repeatR)
library(tidyverse)
library(ape)
library(ggplot2)
library(cowplot)
```

# Effector significance example

# create bed files from RepeatMasker out file

# Ecl
```{r}
Ecl_out <- read_rm_new(RMout_path("Ecl"))
Ecl_out <- group_all_tclass(Ecl_out)

ecl.bed <- rm_to_bed(Ecl_out)
write_bed(ecl.bed, "Ecl/repeat_beds/Ecl_out.bed")
```

use bedtools closest to obtain closest distances for every TE and its closest downstream gene

load in bed bedtools output file and make appropriate column name changes for easy handling

```{r}
Ecl_BT <- read.table("Ecl/results/BEDTOOLS_closest/final/Ecl_a-rep_b-gene_-d-Dref-iu.gff3")
Ecl_BT$V15 <- str_replace(Ecl_BT$V15, "ID=[[:alnum:]]+_", "")
Ecl_BT$V15 <- str_replace(Ecl_BT$V15, ";", "") 
Ecl_BT <- Ecl_BT %>% rename(seqid = V1, start = V2, end = V3,
                tname = V4, gene_id = V15, 
                start.b = V10, end.b = V11, 
                distance = V16)
```

Load in effectors and SM

```{r}
Ecl_effectors <- read_effector_P(effector_path("Ecl"))
Ecl_effectors <- filter(Ecl_effectors, prediction == "Effector")
Ecl_effectors <- Ecl_effectors[,c(1,2)]
Ecl_SM <- read_SM(SM_path("Ecl"))
Ecl_SM$prediction <- "Sec.Metab"
Ecl_sp <- rbind.data.frame(Ecl_effectors, Ecl_SM)
Ecl_sp
```
Make full gene df

```{r}
full_join(Ecl_BT , Ecl_sp)
#replace NAs with "control." Anything that isn't an effector or SM is NA

Ecl_BT_bygene$prediction[is.na(Ecl_BT_bygene$prediction)] <- "Control"
```
one_rep <- function(n){
  df <- Ecl_BT %>% filter(prediction == "Control")
  df <- df[sample(nrow(df), 128),] #size match to 128 effectors
  df1kb <- df %>% filter(distance <= 1000) # get only within 1kb upstream
  group_counts1kb <- df1kb %>%  group_by(prediction) %>% 
    count(group) %>% arrange(group)
  group_counts1kb$rep <- n
  filter(group_counts1kb, prediction =="Control")
}

library(parallel)
null_distr <- bind_rows(mclapply(1:1000, one_rep, mc.cores=1))
null_summ <- summarise(group_by(null_distr, group), lower=quantile(n, c(0.025)), upper=quantile(n, 0.975), median=quantile(n,0.5))

#effectors only
Ecl_BT_effectors <- filter(Ecl_BT, prediction == "Effector")
Ecl_eff_1kb <- Ecl_BT_effectors %>% filter(distance <= 1000)
Ecl_eff1_counts1kb <- Ecl_eff_1kb %>% group_by(prediction) %>% 
    count(group) %>% arrange(group)
#this line does the same as above.
observed <- select(ungroup(filter(Ecl_eff1_counts1kb, prediction =='Effector')), group,n)

result <- full_join(null_summ, observed)
result <- tidyr::replace_na(result,list(lower=0, upper=0, median=0, n=0))
result
```
```{r}
ggplot(result, aes(x=group, y=n)) + geom_col(fill="steelblue") + geom_pointrange(aes(ymin=lower, ymax=upper, y=median),) + coord_flip()
```



